Data Preparation

### 2019-01-10 Data Preparation.Rmd
updating libraries

```{r setup, message = FALSE}
library(tidyverse)
library(tidytext)

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
library(rlist)
```

>>>>

```{r libraries, message = FALSE}
library(tidyverse)
library(tidytext)

library(gsheet) # import spreadsheets from google drive
library(tm)
library(hunspell) # Stemmer
#library(rlist)
```
